---
title: "R Notebook"
output:
  html_document: default
  html_notebook: default
---

First we load our libraries

```{r}
library(jsonlite)
library(dplyr)
library(ggmap)
library(ggplot2)
library(leaflet)
```

Then we read in our data from [New York's Open Data Portal](http://data.ny.gov). Here is the [National Register of Historic Places dataset](https://data.ny.gov/Recreation/National-Register-of-Historic-Places/iisn-hnyv). The data is outputted in a json format, so we use the jsonlite package.

```{r}
url <- "https://data.ny.gov/resource/wtyn-j33w.json"
dat <- fromJSON(url)
head(dat)
```

Now we are going to filter the data for just historic places in Onondaga County.

```{r}
syracuse.landmarks <- dat[dat$county == "Onondaga",]
head(syracuse.landmarks)

```

And finally we will create a map using the leaflet package, which helps us create interactive maps.

```{r}
m <- leaflet() %>%
  setView(lng = -76.125, lat = 43.041, zoom = 10) %>%
  addProviderTiles("CartoDB.Positron") %>%
  addCircleMarkers(lng=syracuse.landmarks$x, lat=syracuse.landmarks$y, popup=syracuse.landmarks$resource_name, clusterOptions = markerClusterOptions())
m
```

